\textit{Extended data for}: Towards human Super EEG?

### 2018-10-11 paper/supporting_information.tex
typo fixes in supporting info to get latex to compile
supporting info updated

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\small \textbf{Reconstruction accuracy predicted by data
    features for each dataset.} \textbf{A.-F. \& G.-L.  Correspondence
    between average
    reconstruction accuracy
    and data feature for datasets 1 and 2.} The scatterplots display the z-transformed
  average patient correlation coefficient versus different features of
  the data (\textbf{A. & G.} total electrodes, \textbf{B. & H.}  proportion thresholded, \textbf{C. & I.} total recording time,
  \textbf{D. & J.}  number thresholded, \textbf{E. & K.}  number of sessions, and \textbf{F. & L.}  average session
  length). The one-dimensional histograms report the distribution of
  the z-transformed correlation coeffiencients and the associated data
feature.}
\label{fig:supplemental_4}
\end{figure}

>>>>

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\small \textbf{Reconstruction accuracy predicted by data
    features for each dataset.} \textbf{A.--F.  Features from Dataset
    1.}  Features include: (\textbf{A.}) number of electrodes,
  (\textbf{B.}) proportion thresholded, (\textbf{C.}), total recording
  time, (\textbf{D.}) number thresholded, (\textbf{E.}) number of
  sessions, and (\textbf{F.}) average session length.
 \textbf{G.--L. Features from Dataset 2.}  Analogous format to
  Panels A--F. The one-dimensional histograms report the distribution of
  the z-transformed correlation coeffiencients and the associated data
feature.}
\label{fig:supplemental_4}
\end{figure}
